EoS-insensitive relations after GW170817

### 2019-02-07 paper/bin-love-after-gw170817.tex
removed comments and fixed Fig 1

\subsection{Executive Summary}
\zc{Me and Kent discussed whether or not we should include this section or not, and we decided like having the quick summary for busy readers - especially with the increasing number of figs and tables (8 tables, 14 figures so far). We can discuss this further if anyone doesn't want it included :)}
{\ny{I'm ok with keeping this, but let's get the science finished first.}}
%What we did
In this paper we attempt to improve I-Love-Q, C-Love, and binary Love relations by imposing constraints on the EoS found by GW170817~\cite{LIGO:posterior,TheLIGOScientific:2017qsa}.
First, we generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, where we (i) impose the restriction that they must be drawn from GW170817s 90\% credible posterior in pressure as a function of density, and (ii) don't impose any restrictions for comparison purposes.
Next, we follow the important works of~\cite{Yagi:binLove} and~\cite{Yagi:ILQ} to show how the ``constrained" set of EoSs show improved universality (binary Love, I-Love-Q, and C-Love) from both the previous works, and the ``unconstrained" sample, shown by Fig.~\ref{fig:ILQ}.
In addition, we determine the degree to which hybrid star EoSs obey binary Love relations.
Finally, through a simple Fisher analysis, we consider the value in improving EoS-insensitive relations by approximating when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in the relations.

%Final Results
Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with mass ratios of $0.75$, in C-Love universality by a factor of $\sim 67\%$, and in I-Love-Q universality by factors of $\sim50$\%, tabulated in Tab.~\ref{tab:maxVar}.
We also present the relationship between the NS radius and tidal deformability, computed directly from the C-Love relations, showing maximum EoS variability of $358.9 \text{ km}$ from the fit discussed in Sec.~\ref{sec:clove}.
Additionally, we find that hybrid quark-hadron stars do obey the I-Love-Q and C-Love relations, with sightly increased EoS variability.
We also find that binaries consisting of one massive hybrid star, and one small-mass hadronic star do not agree with derived binary Love relations, due to the large separation in $\tilde{\Lambda}$ between the constituent stars.
Due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the EoS-insensitive relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors $A \equiv ($ O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, ET~\cite{ET}, CE~\cite{Ap_Voyager_CE}$)$.
Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated interferometer $A$).
These values are further tabulated in Table~\ref{tab:variances}.
It can be seen from this figure that the statistical errors from parameter extraction become comparable the EoS-insensitive relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love relations will become necessary.
Also shown in the figure is the same measurement uncertainties upon the injection of the PhenomD + NRTidal waveform, rather than the PhenomD + 6PN tidal correction to demonstrate the effect of waveform mismodeling.
\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{stackedFisher.eps}
\end{center}
\caption{
Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue circles) in the extraction of $\lambda_0$ from GW170817 (O2 detector sensitivity) as if it were observed with future interferometers aLIGO, A\texttt{+}, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
This is compared to the combined uncertainty $\sigma^A_N$ (turquoise shaded region) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper and lower limits of the expected binary NS merger detection rates for O2, aLIGO, A\texttt{+}, Voyager, CE, and ET-D over 1 observation year.
It can be seen that the statistical errors in the parameter extraction become comparable to the systematics from EoS variation in improved binary Love relations (indigo dashed line) for Voyager CE, and ET.
These results are further tabulated in Table~\ref{tab:variances}.
Additionally shown in the figure are the estimated statistical uncertainties on the extraction of $\lambda_0$ upon the injection of the PhenomD + NRTidal correction waveform (IMRD + NRTidal), rather than the PhenomD + 6PN tidal correction (IMRD + 6PN), in order to demonstrate the effect of waveform mismodeling uncertainties.
The single-detection uncertainties are shown by unfilled blue circles, while the combined detection uncertainties are outlined by dashed maroon.
}
\label{fig:stackedFisher}
\end{figure}

@@

{\ny{Can I see the relative fractional different between each fit and the data for hybrid stars only? (ie. the analogous thing to the green dashed lines of the figure below, but also with the fits to the total set, to just the hybrids and to just the neutron stars.) I wonder whether there is any improvement at all when you fit just to hybrid stars or whether there are any features.}}
{\zc{Nico, Yes of course! I've added a new figure (for example only - this can be removed later) - Fig.~\ref{fig:example} showing the fractional difference for hybrid stars only for the three cases shown in the text. Looking at the figures, they don't change much at all in shape for the first two cases - just a minor vertical shift. The third case (fits to hybrids only) looks different but not by much.}}
{\ny{Ok, this makes more sense to me now. The universality does increase, but only by a small amount (which you did say before -- something like from 1.7 to 1 per cent.). Ok, we can remove these figures and these comments if you'd like. }}
\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{compareHybrid.pdf}
\end{center}
\caption{
\zc{Example figure applying to Nicos comment on the differences between the three different cases of Hybrid star fits: Case I - Complete set of 100 constrained EoSs combined
with the 10 hybrid star EoSs, Case II - Complete set of 100 constrained EoSs alone, Case III - Complete set of 10 hybrid star EoSs alone.}
}
\label{fig:example}
\end{figure}

@@

In addition, Fig.~\ref{fig:rlove} displays the relationship between the NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
This relationship is computed directly from the C-Love relations discussed above as $R(\Lambda)=m/C(\Lambda)$ for observed mass $m=1.48\text{ M}_{\odot}$ from GW170817.
We also present the uncertainty on a NS radius measurement using the C-Love relations in the bottom panel of Fig.~\ref{fig:rlove}, defined as the absolute difference from the fits.
We observe a large suppression in the radius measurement accuracy from the unconstrained set of EoSs to the constrained set, tabulated in Tab.~\ref{tab:maxVar} as the maximal EoS measurement uncertainty.
{\ny{That's a good idea. But it is not immediately obvious that this will help. Kent and I have found that when you look at relations between dimensionless quantities, then the universality is typically stronger than when you use dimensionful quantities (incidentally, this is why the Doneva paper about rapidly-rotating I-Love-Q is wrong, as pointed out by Haris and George).}}

@@

Figure~\ref{fig:binLove} shows the improved binary Love relation for 3 different mass ratios: $q=0.9$, $q=0.75$, and $q=0.5$ for both the constrained and unconstrained sets of EoSs.
\zc{need to decide if using fractional or actual here}
Observe how once again, the constrained set of EoSs show a considerable improvement upon both the unconstrained set of EoSs, as well as the results found in previous works~\cite{Yagi:binLove}.
Additionally, the unconstrained set of EoSs show similar, yet slightly larger EoS variation than was previously found in Ref.~\cite{Yagi:binLove} due to the random sampling taken into account in this analysis.
Once again, the maximum EoS variability (in terms of fractional difference from the fit for comparison purposes) is tabulated in Tab.~\ref{tab:maxVar} for each value of mass ratio.

{\ny{I get why you are plotting the absolute difference but 
\begin{itemize}
\item[(i)] everywhere else in the paper you are plotting the relative fractional difference, so a reader that doesn't pay much attention (and say misses the 1 sentence in the paragraph above -- by the way, I think the caption is wrong and should say the absolute difference instead of the fractional difference, no? --) will look at the axis and say: Wow! 100\% error...that's bad!. This is a problem, I don't have a solution for it (except for reverting to relative fractional differences) but it should not be ignored. 
\item[(ii)] it is hard to see easily what this error means in terms of EoS-variability. Say for example we pick the q=0.9 hybrid star case at Lambdas of 100. I can easily read that there is EoS variability of about 20. But to see if this 20 is a lot or a little, I have to compare with the top figure, from which I get that Lambdaa is about 60 or 70 (if I use a ruler on my computer screen). Now I have to take these two approximate numbers and compare them, but because they are approximate, it's hard to see whether this is a 30 per cent difference, a 50 percent difference or what.
\end{itemize}
}}
{\zc{I agree completely - and I think we should discuss over Skype what should be done for this plot (Both versions (absolute and fractional) are loaded in the images folder, just comment out the image name in the figure to change it.)
Also, the caption is correct - It says that the absolute differences are shown in the plot, while fractional ones are listed in Table III (in order to easily compare to other universal relations and to previous works.)}}

{\ny{I must have missed something. Why do the unconstrained magenta lines extend way passed the constrained green lines? I didn't see this discussed anywhere.}}
{\zc{This is because I've cut all the EoSs off at masses of 1 M$_{\odot}$, and typically the unconstrained EoSs (maroon) have larger ranges of $\Lambda$ than the unconstrained ones. So when we take $\Lambda_1+\Lambda_2$, we end up getting higher values of $\Lambda_s$ for the unconstrained EoSs than we do for the constrained ones.}}
{\ny{Ahh...yes, makes sense. Please add a sentence or two about this in the text.}}
\begin{figure}
\begin{center} 
\includegraphics[width=\linewidth]{binLoveAbsolute.eps}%{binLove.eps}
\end{center}
\caption{
Binary Love relations shown for the constrained EoSs (dotted maroon) and unconstrained EoSs (solid green) for various values of mass ratio: $q=0.9$, $q=0.75$, and $q=0.50$.
In this figure, the top panel displays the EoS-insensitive relations with fits given by Eq.~\ref{eq:binLovefit} shown by dashed black lines (note there are 2 fits for each mass ratio, corresponding to the constrained and unconstrained sets of EoSs), while the bottom 3 panels correspond to the absolute EoS variation for each mass ratio.
Observe how the constrained set of EoSs show a reduction in EoS variation for both the unconstrained set, and from the results shown in Ref.~\cite{Yagi:binLove}.
The maximal EoS variability (shown as a the fractional difference for comparison purposes) for each case is tabulated and compared in Tab.~\ref{tab:maxVar}.
Additionally shown is the binary Love relations for the 10 hybrid star EoSs (dashed bright green curves), as well as the HS fits (dot-dashed blue curves) discussed in Sec.~\ref{sec:binLove-hybrid}.
Observe the large deviations from the fit as the mass ratio $q$ increases, returning near the fit before the transitional pressure at large values of $\Lambda_s$.
This is shown in the bottom three panels as the absolute difference from the NS fit for comparison, while the HS fits show similar EoS variability to the constrained EoSs.
}
\label{fig:binLove}
\end{figure}

\subsubsection{Hybrid quark-hadron stars}\label{sec:binLove-hybrid}
As described in Sec.~\ref{sec:theory}, transitional quark-hadron matter stars undergo first-order phase transitions at pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at the corresponding transitional mass $M_{\text{tr}}$.
These transitions result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq M_{\text{tr}}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote this as ``HS"), and (ii) low-mass ($M \leq M_{\text{tr}}$) hadronic stars with no internal transition to quark matter (we denote this as ``NS"). {\ny{ooohh...I'm not sure I like the acronyms here. NS typically stands for ``neutron star'' of standard type, like what you would construct from an APR EoS. But here by NS you mean a low-mass neutron star specifically. Let's pick a better acronym.}}
{\zc{We can discuss this over Skype - me and Kent like ``NS" because the low-mass branch of the hybrid star EoS \emph{is} actually a nuclear matter ``NS" EoS - these hybrid stars are derived by introducing a transition to standard NS EoSs.}} 
We consider 3 classes of binary systems in this analysis:
\begin{itemize}
\item HS/NS binary: consists of one massive hybrid star, and one small hadronic neutron star,
\item NS/NS binary: consists of two small-mass hadronic neutron stars,
\item HS/HS binary: consists of two massive hybrid stars.
\end{itemize}

@@

This discrepancy between the hybrid and hadronic matter EoSs can be seen in Fig.~\ref{fig:binLove}, where the binary Love relations for the 10 hybrid star EoSs are shown alongside the constrained and unconstrained nuclear matter EoSs.
Observe how the residuals from the fit are quite good at low pressures (large $\Lambda_s$) where the the binaries consist of NS/NS combinations, before reaching the transitional pressure where the deviations become increasingly large ($\sim160$\% for $q=0.90$, $\sim37$\% for $q=0.75$, and $\sim6$\% for $q=0.50$) for HS/HS and HS/NS binaries. {\ny{Why is there a hump for the HS cases in green in Fig. 7?}}{\zc{The hump comes from the transition between NS and HS branches, as I describe in my above comment. If you are referring to the bottom panels of Fig 7, this hump is because I display the fractional difference of the \emph{HS} EoSs from the \emph{NS} fits - to show how badly they fit (although that is not as visible now that we are plotting absolute difference. Instead, I could plot their fractional difference from their own "HS" fits too. We can discuss this.}} {\ny{I was referring to the hump in the top panel (ie. in the R-Love relation). It'd be good to add a sentence to the text that points this hump out and explains it as you did above.}}

@@

We conclude this section with the observation that the hybrid star EoSs do \emph{not} conform to the fits performed on nuclear matter EoSs.
This is not surprising, as the hybrid branch of the EoSs forces inconsistent results between $\Lambda_1$ and $\Lambda_2$ with different masses; an issue not present for the single-star I-Love-Q relations.
By separating the two branches of the hybrid EoSs, we find a new ``hybrid" branch binary Love fit which gives consistent results to that found for the nuclear matter fits. 
{\ny{But wait, the Newtonian limit is not valid for this hybrid branch, since you are not allowed to go to low enough central densities, right? If so, what are you using for the controlling factor? I found the description in the 2 paragraphs above a bit muddled and short. It is not exactly clear to me what the message you were trying to send was.}}
{\zc{You're right - I tried to change this by using leaving the polytropic index (n) as an additional fitting parameter. Doing this gives n=1.7, and all other parameters $>10^7$. The fit looks good but I'm skeptical about those fit values. Additionally, if I set n=0, the fits diverge. Instead, I wrote a few sentences in the paper saying how it doesn't properly limit to the Newtonian case, and how we tried to remedy it. I'm welcome to any suggestions!}} {\ny{Hmmm....ok.}}

@@

{\ny{Super confused about Fig. 1...}}
\kc{me too}
{\zc{Yes, there is a \emph{lot} of info in this figure. The filled blue circles are the statistical uncertainties on $\lambda_0$ for GW170817 as if it had been detected on Detector A=(O2, aLIGO, A+, Voyager, ET, CE), where the x-axis corresponds to the SNR on that detector as if it found GW170817. The filled turquoise region is the combined statistical uncertainty on the detection of $N_A$ events on each detector A, computed using the bulleted process above (moved to the appendix). There is some height to this shaded region because I consider the the upper and lower error bars of the local BNS merger rate $\mathcal{R}$ - giving us a range of $N_A$'s to consider for each detector. We can talk more about this over Skype.}} 
{\ny{I'm happier with this rewrite (makes more sense to me now).}}

>>>>

\subsection{Executive Summary}
%What we did
In this paper we attempt to improve I-Love-Q, C-Love, and binary Love relations by imposing constraints on the EoS found by GW170817~\cite{LIGO:posterior,TheLIGOScientific:2017qsa}.
First, we generate two large samples of spectral EoSs~\cite{Lindblom:2018rfr}, where we (i) impose the restriction that they must be drawn from GW170817s 90\% credible posterior in pressure as a function of density, and (ii) don't impose any restrictions for comparison purposes.
Next, we follow the important works of~\cite{Yagi:binLove} and~\cite{Yagi:ILQ} to show how the ``constrained" set of EoSs show improved universality (binary Love, I-Love-Q, and C-Love) from both the previous works, and the ``unconstrained" sample, shown by Fig.~\ref{fig:ILQ}.
In addition, we determine the degree to which hybrid star EoSs obey binary Love relations.
Finally, through a simple Fisher analysis, we consider the value in improving EoS-insensitive relations by approximating when the statistical errors from parameter extraction become comparable to the systematic errors due to EoS variation in the relations.

%Final Results
Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of $\sim 59$\% for stars with mass ratios of $0.75$, in C-Love universality by a factor of $\sim 67\%$, and in I-Love-Q universality by factors of $\sim50$\%, tabulated in Tab.~\ref{tab:maxVar}.
We also present the relationship between the NS radius and tidal deformability, computed directly from the C-Love relations, showing maximum EoS variability of $358.9 \text{ km}$ from the fit discussed in Sec.~\ref{sec:clove}.
Additionally, we find that hybrid quark-hadron stars do obey the I-Love-Q and C-Love relations, with sightly increased EoS variability.
We also find that binaries consisting of one massive hybrid star, and one small-mass hadronic star do not agree with derived binary Love relations, due to the large separation in $\tilde{\Lambda}$ between the constituent stars.
Due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the EoS-insensitive relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors $A \equiv ($ O2~\cite{aLIGO}, aLIGO~\cite{aLIGO}, A\texttt{+}~\cite{Ap_Voyager_CE}, Voyager~\cite{Ap_Voyager_CE}, ET~\cite{ET}, CE~\cite{Ap_Voyager_CE}$)$.
Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated interferometer $A$).
These values are further tabulated in Table~\ref{tab:variances}.
It can be seen from this figure that the statistical errors from parameter extraction become comparable the EoS-insensitive relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love relations will become necessary.
Also shown in the figure is the same measurement uncertainties upon the injection of the PhenomD + NRTidal waveform, rather than the PhenomD + 6PN tidal correction to demonstrate the effect of waveform mismodeling.
\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{stackedFisher.eps}
\end{center}
\caption{
Estimated statistical uncertainties on the extraction of $\lambda_0$ observed from interferometers $A=$(O2, aLIGO, A\texttt{+}, Voyager, CE, ET-D$)$ as a function of the signal-to-noise-ratio.
In this figure, the filled blue circles denote the single-event statistical uncertainties $\sigma^A_{\text{GW170817}}$ of GW170817 as if it were observed on detector $A$.
Also shown by the turquoise shaded region is combined uncertainty $\sigma^A_N$  from the observation of multiple events from a simulated population of size $N_A$ corresponding to the upper and lower limits of the expected binary NS merger detection rates for O2, aLIGO, A\texttt{+}, Voyager, CE, and ET-D over 1 observation year.
It can be seen that the statistical errors in the parameter extraction become comparable to the systematics from EoS variation in the improved binary Love relations (indicated by the horizontal indigo dashed line) for Voyager, CE, and ET.
These results are further tabulated in Table~\ref{tab:variances}.
Additionally shown in the figure are the estimated statistical uncertainties on the extraction of $\lambda_0$ upon the injection of the PhenomD + NRTidal correction waveform (IMRD + NRTidal), rather than the PhenomD + 6PN tidal correction (IMRD + 6PN), in order to demonstrate the effect of waveform mismodeling uncertainties.
The single-detection uncertainties are shown by unfilled maroon circles, while the combined detection uncertainties are outlined by dashed maroon.
}
\label{fig:stackedFisher}
\end{figure}

@@

@@

In addition, Fig.~\ref{fig:rlove} displays the relationship between the NS radius and tidal deformability for the constrained and unconstrained sets of EoSs.
This relationship is computed directly from the C-Love relations discussed above as $R(\Lambda)=m/C(\Lambda)$ for observed mass $m=1.48\text{ M}_{\odot}$ from GW170817.
We also present the uncertainty on a NS radius measurement using the C-Love relations in the bottom panel of Fig.~\ref{fig:rlove}, defined as the absolute difference from the fits.
We observe a large suppression in the radius measurement accuracy from the unconstrained set of EoSs to the constrained set, tabulated in Tab.~\ref{tab:maxVar} as the maximal EoS measurement uncertainty.

@@

Figure~\ref{fig:binLove} shows the improved binary Love relation for 3 different mass ratios: $q=0.9$, $q=0.75$, and $q=0.5$ for both the constrained and unconstrained sets of EoSs.
Observe how once again, the constrained set of EoSs show a considerable improvement upon both the unconstrained set of EoSs, as well as the results found in previous works~\cite{Yagi:binLove}.
Additionally, the unconstrained set of EoSs show similar, yet slightly larger EoS variation than was previously found in Ref.~\cite{Yagi:binLove} due to the random sampling taken into account in this analysis.
Once again, the maximum EoS variability (in terms of fractional difference from the fit for comparison purposes) is tabulated in Tab.~\ref{tab:maxVar} for each value of mass ratio.

\begin{figure}
\begin{center} 
\includegraphics[width=\linewidth]{binLoveAbsolute.eps}%{binLove.eps}
\end{center}
\caption{
Binary Love relations shown for the constrained EoSs (dotted maroon) and unconstrained EoSs (solid green) for various values of mass ratio: $q=0.9$, $q=0.75$, and $q=0.50$.
In this figure, the top panel displays the EoS-insensitive relations with fits given by Eq.~\ref{eq:binLovefit} shown by dashed black lines (note there are 2 fits for each mass ratio, corresponding to the constrained and unconstrained sets of EoSs), while the bottom 3 panels correspond to the absolute EoS variation for each mass ratio.
Observe how the constrained set of EoSs show a reduction in EoS variation for both the unconstrained set, and from the results shown in Ref.~\cite{Yagi:binLove}.
The maximal EoS variability (shown as a the fractional difference for comparison purposes) for each case is tabulated and compared in Tab.~\ref{tab:maxVar}.
Additionally shown is the binary Love relations for the 10 hybrid star EoSs (dashed bright green curves), as well as the HS fits (dot-dashed blue curves) discussed in Sec.~\ref{sec:binLove-hybrid}.
Observe the large deviations from the fit as the mass ratio $q$ increases, returning near the fit before the transitional pressure at large values of $\Lambda_s$.
This is shown in the bottom three panels as the absolute difference from the NS fit for comparison, while the HS fits show similar EoS variability to the constrained EoSs.
}
\label{fig:binLove}
\end{figure}

\subsubsection{Hybrid quark-hadron stars}\label{sec:binLove-hybrid}
As described in Sec.~\ref{sec:theory}, transitional quark-hadron matter stars undergo first-order phase transitions at pressure $P_{\text{tr}}$, where the hadronic branch departs into a quark-matter branch at the corresponding transitional mass $M_{\text{tr}}$.
These transitions result in two distinct types of NSs, based on their observed mass: (i) massive ($M \geq M_{\text{tr}}$) hybrid stars which have quark-matter cores and nuclear matter crusts (we denote this as ``HS"), and (ii) low-mass ($M \leq M_{\text{tr}}$) hadronic stars with no internal transition to quark matter (we denote this as ``NS").
We consider 3 classes of binary systems in this analysis:
\begin{itemize}
\item HS/NS binary: consists of one massive hybrid star, and one small hadronic neutron star,
\item NS/NS binary: consists of two small-mass hadronic neutron stars,
\item HS/HS binary: consists of two massive hybrid stars.
\end{itemize}

@@

This discrepancy between the hybrid and hadronic matter EoSs can be seen in Fig.~\ref{fig:binLove}, where the binary Love relations for the 10 hybrid star EoSs are shown alongside the constrained and unconstrained nuclear matter EoSs.
Observe how the residuals from the fit are quite good at low pressures (large $\Lambda_s$) where the the binaries consist of NS/NS combinations, before reaching the transitional pressure where the deviations become increasingly large ($\sim160$\% for $q=0.90$, $\sim37$\% for $q=0.75$, and $\sim6$\% for $q=0.50$) for HS/HS and HS/NS binaries.

@@

We conclude this section with the observation that the hybrid star EoSs do \emph{not} conform to the fits performed on nuclear matter EoSs.
This is not surprising, as the hybrid branch of the EoSs forces inconsistent results between $\Lambda_1$ and $\Lambda_2$ with different masses; an issue not present for the single-star I-Love-Q relations.
By separating the two branches of the hybrid EoSs, we find a new ``hybrid" branch binary Love fit which gives consistent results to that found for the nuclear matter fits.

@@
